Brother, Can You Spare a Manufacturing Job?  How Voters React to Deindustrialization

### 2021-12-11 Final Draft/Final Draft.Rmd
tweaks

\begin{figurenotes}
Calculated as net change in manufacturing employment from 2004-2015 divided by 2004 total employment.
\end{figurenotes}
\end{figure}

@@

Using this instrument, we then conduct a two stage regression. First we estimate manufacturing job loss with the Bartik Instrument and a set of county-level controls; then we use the estimated values of job losses to predict Democratic vote share. In these regressions we control for unemployment, service layoffs, the share of college-educated voters, and the share of male voters. For some estimates, we also control for the white share of the population. We also apply state fixed effects to account for a wide variety of state-level changes from 2012-2016 (such as voter suppression tactics). These controls are similar to those of \cite{Baccini21}.

@@

This coefficient is still somewhat difficult to interpret, and made increasingly so by the winner-take-all system by which U.S. Electoral College votes are allocated. As an alternative perspective, we examined a range of counterfactual scenarios, in which counties experienced job losses

@@

#  make map
flipped <- mapping_small %>% filter(changed_outcome == "Yes")
ggplot() +
  geom_sf(data = mapping_small, aes(fill = delta_vs_group), color = "black", size = .1) +
  scale_fill_manual(values = colors) +
  labs(title = "Figure 3: Impact of Manufacturing Job Lossess on Democratic Vote Share",
       subtitle = "Change in Democratic Vote Share Assuming 25th Percentile of Manufacturing Job Losses",
       fill = "Change in Democratic Vote Share") +
  geom_sf(data = flipped, fill = NA, 
          aes(color = changed_outcome), 
          size = 1) +
  scale_color_manual(values = "#b32ab5", name = "Flipped Election") +
  labs(color = "Flipped Election") +
  coord_sf(datum = NA) +
  theme_minimal() +
  # geom_sf_text_repel(aes(label = state), data = mapping_small,
  #                    force = .00001,  seed = 10,
  #                    size = 2.5) +
  theme(  axis.title.x=element_blank(),
          axis.title.y=element_blank())

```
\begin{figurenotes}
Gain or loss of national manufacturing jobs, divided by total national workforce.
\end{figurenotes}
\end{figure}

XXXXXXXXXXXXXXXXXXXXXX EXPLAIN COUNTERFACTUAL

>>>>

\end{figure}

@@

Using this instrument, we then conduct a two-stage regression. First we estimate manufacturing job loss with the Bartik Instrument and a set of county-level controls; then we use the estimated values of job losses to predict Democratic vote share. In these regressions we control for unemployment, service layoffs, the share of college-educated voters, and the share of male voters. For some estimates, we also control for the white share of the population. We also apply state fixed effects to account for a wide variety of state-level changes from 2012-2016 (such as voter suppression tactics). These controls are similar to those of \cite{Baccini21}.

@@

This coefficient is still somewhat difficult to interpret, and made increasingly so by the winner-take-all system by which U.S. Electoral College votes are allocated. As an alternative perspective, we examined a range of counterfactual scenarios, in which counties experienced job losses
XXXXXXXXXXXXXXXXXXXXXX EXPLAIN COUNTERFACTUAL

@@

#  make map
flipped <- mapping_small %>% filter(changed_outcome == "Yes")
ggplot() +
  geom_sf(data = mapping_small, aes(fill = delta_vs_group), color = "black", size = .1) +
  scale_fill_manual(values = colors) +
  labs(title = "",
       subtitle = "",
       fill = "Change in Democratic Vote Share") +
  geom_sf(data = flipped, fill = NA, 
          aes(color = changed_outcome), 
          size = 1) +
  scale_color_manual(values = "#b32ab5", name = "Flipped Election") +
  labs(color = "Flipped Election") +
  coord_sf(datum = NA) +
  theme_minimal() +
  # geom_sf_text_repel(aes(label = state), data = mapping_small,
  #                    force = .00001,  seed = 10,
  #                    size = 2.5) +
  theme(  axis.title.x=element_blank(),
          axis.title.y=element_blank())

```
\end{figure}
